Plot the within and between group distance in a bar plot

### 2020-01-28 scripts/33_distance_bar.Rmd
update

@@

tibble(
  N_dist_mean = N_dist_mean,
  Y_dist_mean = Y_dist_mean,
  NY_dist_mean =  NY_dist_mean
) %>% 
  gather(key = 'group', value  = 'mean_dist') %>% 
  mutate(mean_dist = round(mean_dist, 0)) %>% 
  ggbarplot(x = 'group', y = 'mean_dist', label = T,
            color = 'white', fill = 'forestgreen',
            title = 'euclidean distance within and between group')
```

>>>>

```{r}
# do the same thing as below but with matrix that only have enterococcos and ...
pw_fil <- bact_matrix
```

@@

# tibble(
#   N_dist_mean = N_dist_mean,
#   Y_dist_mean = Y_dist_mean,
#   NY_dist_mean =  NY_dist_mean
# ) %>% 
#   gather(key = 'group', value  = 'mean_dist') %>% 
#   mutate(mean_dist = round(mean_dist, 0)) %>% 
#   ggbarplot(x = 'group', y = 'mean_dist', label = T,
#             color = 'white', fill = 'forestgreen',
#             title = 'euclidean distance within and between group')

all <- bind_rows(data_frame(group = 'NY',distance = dists@dist),
    data_frame(group = 'N',distance = N_dist),
    data_frame(group = 'Y',distance = Y_dist))

all %>% 
  ggboxplot(x = 'group', y = 'distance', add = 'jitter') +
  stat_compare_means(
    comparisons = list(c('NY', 'N'), c('NY','Y'), c('Y','N')),
    label = "p.signif",
    method = 'wilcox.test') +
  ggsave('../figs/distance/bact.jpg', dpi = 300, width = 6 , height = 5)
```
